\documentclass[11pt]{article}
% Default margins are too wide all the way around. I reset them here
\setlength{\topmargin}{-.5in}
\setlength{\textheight}{9in}
\setlength{\oddsidemargin}{.125in}
\setlength{\textwidth}{6in}

\usepackage{url}
\usepackage{amsmath}
\usepackage{color}
\usepackage{graphicx}

\newcommand{\textred}[1]{\textcolor{red}{#1}}
\ifx\noeditingmarks\undefined
  \newcommand{\pgwrapper}[2]{\textbf{#1: }\textred{#2}}
\else
  \newcommand{\pgwrapper}[2]{}
\fi
\newcommand\todo[1]{\textcolor{red}{#1}}
\newcommand\RED[1]{\textcolor{red}{#1}}
\newcommand\BLUE[1]{\textcolor{blue}{#1}}
\newcommand\GREEN[1]{\textcolor{brown}{#1}}
\newcommand{\para}[1]{\smallskip\noindent {\bf #1}}

\begin{document}
\title{Agent: Find Your Expert}
\author{
  Brandon Li\\
  Chris Zheng \\
  Daniel Tahara\\ \\
  {\it Yale University}\\
  \{brandon.li, chris.zheng, daniel.tahara\}@yale.edu
}
\renewcommand{\today}{}
\maketitle

\section{Introduction}
\label{sec:intro}
As people increasingly eschew traditional, physical information sources such as
books and television, they turn to internet for information of all forms,
whether they be tutorials, videos, or encyclopedia entries. Yet as they turn to
the internet for its ease of use, they increasingly expect curated or summarized
content instead of the original source material. This has manifested itself in a
number of ways. One trend we have seen is the proliferation of free,
question-and-answer sites (let alone message boards and other sites).  Yahoo
Answers~\cite{yahoo} is among the most well of these sites, allowing users to
post arbitrary (not necessarily fact-based) questions to which anyone can
respond. Of course, in exchange for ease of use and a broad audience comes a
large amount of noise and spam, so other companies have a) created
domain-specific, micro-sites sites like those in the StackExchange\cite{stackx}
network, and/or b) augmented the question-and-answer model with an extensive
reputation system, so that only reputable and qualified users can respond to
questions (examples include StackExchange sites as well as Quora~\cite{quora}).

However, just as these sites because of their abilities to reach large
audiences, so too do they fall short because of the inability to communicate
synchronously (e.g.\ to clarify an explanation) and the lack of any real
incentive for individuals to provide content. Thus, we have also seen the
development of paid information retrieval services such as
Cha-Cha~\cite{chacha}, kgb~\cite{kgb}, and even the commodotization of those
services through sites such as Amazon's Mechanical Turk~\cite{turk}.

A fundamental limitations of question-and-answer sites (and even the internet as
a whole) is that while it is a nearly infinite repository of information, it
does not, and perhaps cannot, capture the full extent of knowledge---the
understanding of information and associations between things---of the
contributing users. Projects such as IBM Watson~\cite{watson} and Google
Knowledge Graph~\cite{knowledge}, as well as the development of the Resource
Description Framework~\cite{rdf} are a step toward a knowledge-based, semantic,
web, but their usefulness is limited to certain, well-defined tasks.

Enter Agent. Rather than automating the process of knowledge gathering, Agent
identifies the individuals within your social networks who are most likely to be
able to provide knowledge about a particular topic. By recommending experts
from people you actually know, Agent improves your ability to get a timely,
personal response, and allows you to establish a more meaningful dialogue about
a topic than allowed by one-off, question-and-answer formats or pre-written
articles. Agent brings you knowledge through the web.

\input{features}
\input{architecture}
\input{data-model}
\input{scoring-algorithm}

\section{Conclusion}
\label{sec:conclusion}
\todo{BLi or Chris}

\bibliographystyle{plain}
\bibliography{ref}
% That's all folks!
\end{document}

